Implementation and Evaluation of Routing Algorithm in GENI Software-Defined Networking

### 2018-06-11 paper.tex
update

        \qquad OpenFlow is a communications protocol between SDN controller and OpenFlow switch that enables the SDN 

@@

      	\end{figure}
     \begin{figure}[p]
          \centering
          \caption{The example of the function which handle the packet}
          	\includegraphics[width=1.0\textwidth]{packet_in_handler.png}
      	\end{figure}
  \chapter{Implementation of Routing Algorithm in GENI}
  	\section{The reservation of compute resources for customized topology}
		\qquad In GENI, There are three methods to reserve the resources: (a) setting the topology manually; (b) choose existing topology; (c) import Resouce spectification (Rspec) documents. Figure 4.1 to Figure 4.3 show the three methdos to reserve the resources. In (a), you could just drag the components into the screen and create the topology you desire. In (b) choosing the existing topology that the geni offering. In (c) To use the Rspec documents, you could write a program to output the Rspec document by following the Rspec structure.
		\begin{figure}
          \caption{(a) Setting the topology manually.}
          \centering
            \includegraphics[width=1.0\textwidth]{geni_manual.png}
          \caption{(b) Choose existing topology.}
            \includegraphics[width=1.0\textwidth]{choose_existing.png}
          \caption{(c) Import Resouce spectification (Rspec) documents.}
            \includegraphics[width=1.0\textwidth]{rspec_format.png}
      	\end{figure}
   \section{Offline algorithm}
     \subsection{create the network graph for the input of routing algorithm}
     \qquad After reserve the resources, copy the network structure document from GENI online website. Fugure 4.4 shows the the network structure document. The network structure document contains the information of nodes and links. Using this document to create the netowrk graph for the input of the routing algorithm.
     \begin{figure}
        \caption{The network structure in GENI}
        \centering
          \includegraphics[width=1.0\textwidth]{Raw_resource.png}
     \end{figure}
     \subsection{setting up the demands}
     \qquad After the routing algorithm compute the pathes of the demands. In order to let the Open vSwitch to identify each demands, we use ip of source, ip of destination, port of destination to identify each demands.
 For each nodes, we create a script to run the demands with given information. 
 	\subsection{setting up the controller}
 	\qquad For controller, we create a dictionary for it. Every time when a node asks the controller how to process the demands, controller could use ip of source, ip of destination, port of destination as a key to find the path of the demand then send the OpenFlow message to the switch for adding the flow into the flow table. 
 	\section{Online algorithm}
 		\subsection{ryu controller}
 		\qquad In ryu controller, we need to implement a topology discovery which the routing algorithm could use. Figure 4.5 is the package which the Ryu controller need to import. Figure 4.6 is the code to discover topology.
 		\begin{figure}
          \caption{Ryu controller import package for topology discovery.}
          \centering
            \includegraphics[width=1.0\textwidth]{ryu_import.png}
          \caption{The code of topology discovery in Ryu controller.}
            \includegraphics[width=1.0\textwidth]{ryu_discovery.png}
      	\end{figure}
  \chapter{Case study}
  \chapter{Experiment results}
  \chapter{Summary}
    \section{conclusion}
    \section{future work}
  \chapter{References}
     \end{large}
    \end{document}

>>>>

      \qquad OpenFlow is a communication protocol between SDN controller and OpenFlow switch that enables the SDN 

@@

	          \caption{The example of the function which handle the packet}
	          	\includegraphics[width=1.0\textwidth]{packet_in_handler.png}
  \chapter{Implementation of Routing Algorithm in GENI}
	  	\section{The reservation of compute resources for customized topology}
			\qquad In GENI, There are three methods to reserve the resources: (a) setting the topology manually; (b) choose existing topology; (c) import Resouce spectification (Rspec) documents. Figure 4.1 to Figure 4.3 show the three methdos to reserve the resources. In (a), you could just drag the components into the screen and create the topology you desire. In (b) choosing the existing topology that the geni offering. In (c) To use the Rspec documents, you could write a program to output the Rspec document by following the Rspec structure.
	          \caption{(a) Setting the topology manually.}
	            \includegraphics[width=1.0\textwidth]{geni_manual.png}
	          \caption{(b) Choose existing topology.}
	            \includegraphics[width=1.0\textwidth]{choose_existing.png}
	          \caption{(c) Import Resouce spectification (Rspec) documents.}
	            \includegraphics[width=1.0\textwidth]{rspec_format.png}
	   \section{Offline algorithm}
	     \subsection{create the network graph for the input of routing algorithm}
	     \qquad After reserving the resources, copy the network structure document from GENI online website. Fugure 4.4 shows the the network structure document. The network structure document contains the information of nodes and links. Using this document to create the netowrk graph for the input of the routing algorithm.
	        \caption{The network structure in GENI}
	          \includegraphics[width=1.0\textwidth]{Raw_resource.png}
	     \subsection{setting up the demands}
	     \qquad After the routing algorithm compute the pathes of the demands. In order to let the Open vSwitch to identify each demands, we use ip of source, ip of destination, port of destination to identify each demands.
	 For each nodes, we create a script to run the demands with given information. 
	 	\subsection{setting up the controller}
	 	\qquad For controller, we create a dictionary for it. Every time when a node asks the controller how to process the demands, controller could use ip of source, ip of destination, port of destination as a key to find the path of the demand then send the OpenFlow message to the switch for adding the flow into the flow table. 
	 	\section{Online algorithm}
	 		\subsection{ryu controller}
	 		\qquad In ryu controller, we need to implement a topology discovery which the routing algorithm could use. Figure 4.5 is the package which the Ryu controller need to import. Figure 4.6 is the code to discover topology. After the controller gets the topology, every time when a packet sends to the controller, we parse the information of the packet. Getting its ip source, ip destination, destination port as the demand's key. Input this key and topology into the algorithm then get the path output by controller. Sending the messages to the switch to add the flow in the flow table.
	          \caption{Ryu controller import package for topology discovery.}
	            \includegraphics[width=1.0\textwidth]{ryu_import.png}
	          \caption{The code of topology discovery in Ryu controller.}
	            \includegraphics[width=1.0\textwidth]{ryu_discovery.png}
  \chapter{Case study}
  \section{Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks}
    \qquad In this section, we study the Maximum Concurrent Flow Problem in MPLS-based Software Defined Networks and implement four algorithms in GENI. Because the MPLS is a per-flow routing, the number of flow paths through a node (switch) needs to be bounded due to the limited ternary content addressable memory (TCAM). Therefore, the problem term to be bounded path-degree maximum concurrent flow problem (BPMCF)
    \subsection{Problem definition}
    \qquad Given a network topology G = (V, E) with link link capacity (bandwidth capacity) 
  \chapter{Experiment results}
  \chapter{Summary}
    \section{conclusion}
    \section{future work}
  \chapter{References}
  \end{large}
  \end{document}
